\cvsection{Projects}
\cvproject{\href{https://github.com/Noovolari/leapp}{Noovolari Leapp} (contributions)}
\begin{itemize}
\item Leapp is a tool for developers to manage, secure, and gain access to any cloud. From setting up your access data to activating a session, Leapp can help manage the underlying assets to let you use your provider's CLI or SDK seamlessy.
\end{itemize}
\smallskip
\smallskip
\cvproject{\href{https://libriusatiunipv.altervista.org}{LibriUsatiUNIPV}}
\begin{itemize}
\item Wordpress website focusing on textbooks exchange within University of Pavia Faculty of Engineering. Developed and managed in collaboration with a friend, was a very successfull project, we had a peak of 598 unique visitors in 10/2019 with almost no advertising.
\end{itemize}
\cvproject{\href{https://github.com/pusi77/eBookPriceComparison}{eBookPriceComparison}}
\begin{itemize}
\item Python script to search and compare eBooks prices and DRMs from my favourite stores. It uses \textit{beautifulsoup4} and \textit{asyncio} for web scraping and \textit{tabulate} to print results.
\end{itemize}
\smallskip
\smallskip
\cvproject{\href{https://github.com/pusi77/Adler32_MIPS}{Adler32\_MIPS}}
\begin{itemize}
\item Adler32 checksum algorithm implementation in MIPS Assembly, developed using MARS MIPS Simulator.
\end{itemize}
\smallskip
\smallskip


\cvsection{Interests}
\cvproject{Technical}
\begin{itemize}
\item Networking.
\item Decentralised computing.
\end{itemize}
\smallskip
\cvproject{Hobbies}
\begin{itemize}
\item Reading comics, manga, graphic novels.
\item DIY and tinkering with technology.
\item Hiking.
\end{itemize}


\cvsection{Languages}
\begin{itemize}
 \item \cvskill {Italian}{5}
 \item \cvskill {English}{3}
 \item \cvskill {Spanish}{1}
\end{itemize}
